Events

### 2024-08-28 notebooks/events/e7.qmd
update event 8

-   [WHPI - Campaign: PSP 7th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp7p.php)
-   [ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 04](http://helioweather.net/missions/psp/per04/)

>>>>

-   [WHPI - Campaign: PSP 7th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp7p.php)
-   [ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 07](http://helioweather.net/missions/psp/per07/)
